\documentclass{software_engineer_rustin_liu}

\newcommand{\en}[1]{#1}
\newcommand{\zh}[1]{}

\zh{\usepackage{xeCJK}}
\zh{\setCJKmainfont{Source Han Serif CN}}
\zh{\setCJKsansfont{Source Han Sans CN}}
\zh{\setCJKmonofont{Source Han Sans CN}}

\begin{document}

\setlength{\baselineskip}{1.2\baselineskip}

\name{\en{Rustin Liu}\zh{刘东坡}}
\basicInfo{
      \email{rustin.liu@gmail.com} \textperiodcentered\
      \phone{+(86) 189-0839-4732} \textperiodcentered\
      \github[hi-rustin]{https://github.com/hi-rustin} \textperiodcentered\
      \homepage[hi-rustin.rs]{https://hi-rustin.rs/}
}

\section{\faGraduationCap\ \en{Education}\zh{教育经历}}
\en{\datedsubsection{\textbf{Software Engineering Bachelor's Degree}}{Sep 2015 -- June 2019}}
\zh{\datedsubsection{\textbf{软件工程 本科}}{2015/09 -- 2019/06}}
\begin{itemize}
      \item \en{Chongqing University of Technology}
            \zh{重庆理工大学}
\end{itemize}

\section{\faCogs\ \en{Skills}\zh{技能}}
\begin{itemize}[parsep=0.25ex]
      \item \en{\textbf{Programming Languages}:
                  Experienced in Go/Rust/JavaScript,
                  \textbf{multilingual} (can adapt to any language)}
            \zh{\textbf{编程语言}:
                  熟悉 Go/Rust/JavaScript
                  \textbf{泛语言}（编程不受特定语言限制）}

      \item \en{\textbf{Development Tools}:
                  familiar with Linux-based programming,
                  have experience with tools like Git, GitHub, Docker, Jenkins, Github Actions and Jira, etc.}
            \zh{\textbf{开发工具}:
                  熟悉 Linux，有 Git、GitHub、Docker、Jenkins、Github Actions 和 Jira 等团队协作工具的使用经验}

      \item \en{\textbf{Languages}:
                  \textbf{English} (Can read, write and speak fluently),
                  \textbf{Chinese} (Native speaker)}
            \zh{\textbf{语言}:
                  \textbf{英语} （可以流利的听说读写），
                  \textbf{中文} （母语）}
\end{itemize}

\section{\faUsers\ \en{Work Experience}\zh{工作经历}}

\en{\datedsubsection{\textbf{\href{https://pingcap.com/en/}{PingCAP Inc. - Database - Database Kernel R\&D(Golang/Rust)}}}{August 2023 -- Present}}
\zh{\datedsubsection{\textbf{\href{https://pingcap.com/zh/}{PingCAP Inc. - 数据库 - 数据库内核研发（Golang/Rust）}}}{2023/08 -- 至今}}
\en{\textsl{Transferred from the data platform department to the kernel computing department and started to focus on the development of the optimizer of the distributed database {\href{https://github.com/pingcap/tidb}{TiDB}}.}}
\zh{\textsl{从数据平台部门转组到计算内核部门，开始专注于分布式数据库 {\href{https://github.com/pingcap/tidb}{TiDB} 优化器的研发。}}}

\en{\textbf{Responsibilities:}}
\zh{\textbf{职责：}}
\begin{itemize}
      \item \en{Designed, implemented and maintained the optimizer of the distributed database TiDB.}
      \zh{设计、实现和维护分布式数据库 TiDB 的优化器。}
\end{itemize}

\en{\textbf{Accomplishments:}}
\zh{\textbf{产出：}}
\begin{itemize}
      \item \en{Added support for the LOCK STATS TABLE feature to allow users to lock statistics updates and generate stable execution plans.}
      \zh{添加 LOCK STATS TABLE 功能，方便用户锁定统计信息的更新，生成稳定的执行计划。}
      \item \en{Deleted a large number of deprecated code, greatly improving the maintainability of the code.}
      \zh{删除了大量弃用功能代码，极大的改善了代码可维护性。}
\end{itemize}

\en{\datedsubsection{\textbf{\href{https://pingcap.com/en/}{PingCAP Inc. - Database - Database Tools R\&D(Golang/Rust)}}}{July 2021 -- July 2023}}
\zh{\datedsubsection{\textbf{\href{https://pingcap.com/zh/}{PingCAP Inc. - 数据库 - 数据库工具研发（Golang/Rust）}}}{2021/07 -- 2023/07}}
\en{\textsl{Transferred from the community department to the data platform department and started to focus on the development of data synchronization tools {\href{https://github.com/pingcap/tiflow}{TiCDC}}.}}
\zh{\textsl{从社区部门转组到数据平台部门，开始专注于数据同步工具 {\href{https://github.com/pingcap/tiflow}{TiCDC} 的研发。}}}

\en{\textbf{Responsibilities:}}
\zh{\textbf{职责：}}
\begin{itemize}
      \item \en{Designed, implemented, and maintained core modules, focusing on Sink and Sorter, and managed daily project maintenance including issue tracking, code reviews, and on-call customer support.}
            \zh{设计、实现和维护核心模块，专注于 Sink 和 Sorter，管理项目日常维护，包括 issue 追踪、代码审阅和 on-call 客户支持。}
\end{itemize}

\en{\textbf{Accomplishments:}}
\zh{\textbf{产出：}}
\begin{itemize}
      \item \en{Changed push mode to pull mode to optimize memory management and data synchronization process, greatly improving OOM issues and synchronization lags.}
            \zh{将推送模式修改为了拉取模式优化了内存管理和数据同步流程，极大的改善了 OOM 问题和同步延迟。}
      \item \en{Modified the Sink module from synchronous to asynchronous mode to optimize code performance and improve throughput by 30\% in incremental scenarios.}
            \zh{将 Sink 模块从同步模式修改为异步模式，优化代码性能，将增量场景下吞吐提升 30\%。}
      \item \en{ Added multi-topic and OAuth authorization support for Kafka Sink, greatly reducing the operation and maintenance costs of multi-topic tasks.}
            \zh{为 Kafka Sink 支持了多 Topic 和 OAuth 授权功能，极大的降低了多 Topic 的任务运维成本。}
      \item \en{Added the ability to optimize the Lossy DDL from full table scan to not synchronizing any data, greatly reducing the impact of DDL on the system.}
            \zh{将有损 DDL 从全表扫描优化为不同步任何数据，极大的降低了有损 DDL 对系统的影响。}
      \item \en{Refactored all of TiCDC’s CLI code to standardize the way commands are added and written, which greatly improved maintainability.}
            \zh{重构了 TiCDC 的 CLI 所有代码，标准化了命令添加和编写方式，极大提升了可维护性。}
\end{itemize}

\en{\datedsubsection{\textbf{\href{https://pingcap.com/en/}{PingCAP Inc. - Database - Full-Stack Engineer(Golang/JS)}}}{Aug 2020 -- July 2021}}
\zh{\datedsubsection{\textbf{\href{https://pingcap.com/zh/}{PingCAP Inc. - 数据库 - 前后端开发工程师（Golang/JS）}}}{2020/08 -- 2021/07}}
\en{\textsl{Joined the community department to develop {\href{https://github.com/ti-community-infra/tichi}{TiChi}} to support community collaboration based on the Kubernetes Community{\href{https://github.com/kubernetes/test-infra/tree/master/prow}{ Prow}} project.}}
\zh{\textsl{加入了社区部门，以 Kubernetes 社区{\href{https://github.com/kubernetes/test-infra/tree/master/prow}{ Prow}} 项目为基础开发{\href{https://github.com/ti-community-infra/tichi}{ TiChi}} 来支撑社区协作。}}

\en{\textbf{Responsibilities:}}
\zh{\textbf{职责：}}
\begin{itemize}
      \item \en{Designed and implemented a project with collaborative robots on GKE using Prow, optimizing community collaboration processes for open source contributors.}
            \zh{使用 Prow 在 GKE 上设计和实现一个协作机器人项目，优化开源贡献者的社区协作流程。}
\end{itemize}

\en{\textbf{Accomplishments:}}
\zh{\textbf{产出：}}
\begin{itemize}
      \item \en{Completed TiChi, which has become the company’s CI/CD infrastructure, on time.}
            \zh{按时完成了项目的设计和开发，TiChi 已经成为了公司 CI/CD 的基础设施。}
      \item \en{Fixed bugs and added features for Prow, submitted 39 PRs.}
            \zh{为 Prow 修复 bug 和添加功能，提交了 39 个 PR。}
      \item \en{Added multiple language documents for collaboration process and TiChi.}
            \zh{为 TiChi 编写了良好的文档，明确了协作流程，为开源贡献者提供了更好的协作体验。}
\end{itemize}

\en{\datedsubsection{\textbf{\href{https://www.morningstar.com/}{Morningstar, Inc. - Financial Services - Full-Stack Engineer(Java/JS)}}}{June 2019 -- July 2020}}
\zh{\datedsubsection{\textbf{\href{https://www.morningstar.com/}{晨星资讯（Morningstar, Inc.）- 金融服务 - 前后端开发工程师（Java/JS）}}}{2019/06 -- 2020/07}}
\en{\textsl{First job after graduation, responsible for writing and maintaining data presentation components, left after the company decided to start closing its China R\&D center.}}
\zh{\textsl{毕业后第一份工作，负责编写和维护数据展示组件，在公司决定开始关闭中国研发中心后离职。}}

\en{\textbf{Responsibilities:}}
\zh{\textbf{职责：}}
\begin{itemize}
      \item \en{Developed and optimized front and back-end components in Java and Vue, enhancing engineering efficiency and front-end infrastructure.}
            \zh{使用 Java 和 Vue 开发和优化前后端组件，提升工程效率和前端基础设施。}
\end{itemize}

\en{\textbf{Accomplishments:}}
\zh{\textbf{产出：}}
\begin{itemize}
      \item \en{Independently developed components that are already online, with good stability and performance.}
            \zh{多个独立开发的组件已经上线使用，有较好的稳定性和性能。}
      \item \en{Implemented a front-end tracking system that uses HeapIO to track user information, with an extensible interface to seamlessly switch to Google Analytics.}
            \zh{实现了前端的 tracking 系统，使用 HeapIO 追踪用户信息，并预留可扩展接口，可无缝切换至 Google Analytics。}
      \item \en{Wrote automated Jenkins scripts for component and document releases, optimizing the release process from a manual 4-hour process to a fully automated 30-minute process.}
            \zh{为组件和文档发布编写了自动化 Jenkins 脚本，将发布流程从手动 4 小时优化到全自动 30 分钟。}
\end{itemize}

\section{\faGithubAlt\ \en{Open Source Projects}\zh{开源项目}}
\en{\datedsubsection{\textbf{Cargo - Active Contributor}}{{\href{https://github.com/search?q=repo:rust-lang/cargo+repo:rust-lang/rust+author:hi-rustin&type=commits}{260+ commits}}}}
\zh{\datedsubsection{\textbf{Cargo - 活跃贡献者}}{{\href{https://github.com/search?q=repo:rust-lang/cargo+repo:rust-lang/rust+author:hi-rustin&type=commits}{260+ commits}}}}
\en{\textsl{The Rust package manager. Cargo downloads your Rust package’s dependencies, compiles your packages, makes distributable packages.}}
\zh{\textsl{Rust 包管理器，Cargo 下载 Rust 包的依赖，编译包，制作可分发的包。}}

\begin{itemize}
      \item \en{Improved various error prompts for Cargo commands and the Rust compiler to make errors to effective and clear.}
            \zh{改善了大量 Cargo 命令和 Rust 编译器的错误提示，让错误更有效更清晰。}
      \item \en{Added the --crate-type function and added related documentation for Cargo.}
            \zh{为 Cargo 添加了 --crate-type 功能和相关文档。}
      \item \en{Added support for automatic inheritance of the [workspace.package] fields for the cargo new/init commands.}
            \zh{为 cargo new 和 cargo init 命令支持了 [workspace.package] 字段自动继承。}
      \item \en{Added new syntax for Cargo build scripts to provide a foundation for future extensions to build scripts.}
            \zh{为 Cargo 构建脚本添加新的语法，为未来扩展构建脚本提供基础。}
      \item \en{Added `target.'cfg(..)'.linker` configuration option to allow users to specify the linker via `cfg(..)' conditions.}
            \zh{添加了 `target.'cfg(..)'.linker` 配置项，允许用户通过 `cfg(..)' 条件来指定链接器。}
      \item \en{Added OR\_PATTERNS\_BACK\_COMPAT lint to help users migrate to the new or\-patterns syntax.}
            \zh{添加了 OR\_PATTERNS\_BACK\_COMPAT lint 来帮助用户迁移至新的 or\-patterns 语法。}
      \item \en{Made authors field optional in Cargo and rustdoc.}
            \zh{使 authors 字段在 Cargo 和 rustdoc 中可选。}
\end{itemize}

\en{\datedsubsection{\textbf{cargo-information - Author}}{{\href{https://github.com/hi-rustin/cargo-information}{270+ commits}}}}
\zh{\datedsubsection{\textbf{cargo-information - 作者}}{{\href{https://github.com/hi-rustin/cargo-information}{270+ commits}}}}
\en{\textsl{cargo-info is a tool that provides detailed information about a Rust package.}}
\zh{\textsl{cargo-info 是一个提供 Rust 包详细信息的工具。}}

\begin{itemize}
      \item \en{Works with all registries that are compatible with Cargo.}
            \zh{兼容所有与 Cargo 兼容的注册中心。}
      \item \en{Fetches and displays basic package information (name, version, owners, etc.)}
            \zh{获取并显示基本的包信息（名称、版本、所有者等）。}
      \item \en{Shows package dependencies and their versions.}
            \zh{显示包依赖及其版本。}
      \item \en{Provides information about package features.}
            \zh{提供包的 features 信息。}

\end{itemize}


\en{\datedsubsection{\textbf{crates.io - Maintainer}}{{\href{https://github.com/rust-lang/crates.io/commits?author=hi-rustin}{60+ commits}}}}
\zh{\datedsubsection{\textbf{crates.io - 维护者}}{{\href{https://github.com/rust-lang/crates.io/commits?author=hi-rustin}{60+ commits}}}}
\en{\textsl{The Rust package registry.}}
\zh{\textsl{Rust 包管理中心。}}

\begin{itemize}
      \item \en{Helped implement RFC 3052 to allow crates.io to accept packages without author information.}
            \zh{帮助实现 RFC 3052，让 crates.io 开始接受无作者信息的包。}
      \item \en{Added support for renaming packages with underscore prefixes to be published on crates.io.}
            \zh{支持下划线前缀的重命名包在 crates.io 的发布。}
      \item \en{Aligned crates.io and Cargo on the naming rules for features and crates.}
            \zh{对齐了 crates.io 和 Cargo 对 feature 和 crate 的名称校验规则。}
      \item \en{Fixed flaky tests and improved documentation to improve code maintainability.}
            \zh{修复不稳定测试，完善文档，提升代码可维护性。}
\end{itemize}


\en{\datedsubsection{\textbf{Rustup - Previous Maintainer}}{{\href{https://github.com/rust-lang/rustup/commits?author=hi-rustin}{110+ commits}}}}
\zh{\datedsubsection{\textbf{Rustup - 前维护者}}{{\href{https://github.com/rust-lang/rustup/commits?author=hi-rustin}{110+ commits}}}}
\en{\textsl{Rustup is an installer for Rust. Rustup installs The Rust Programming Language from the official release channels, enabling you to easily switch between stable, beta, and nightly compilers and keep them updated.}}
\zh{\textsl{Rustup 是 Rust 的安装器。Rustup 从官方发布渠道安装 Rust 编程语言，使用户可以轻松地在稳定版、测试版和夜版编译器之间切换并保持更新。}}

\begin{itemize}
      \item \en{Different modes of self-update were supported for Rustup to provide a better experience.}
            \zh{为 Rustup 支持了 self-update 的不同模式来提供更好的使用体验。}
      \item \en{Improved Rustup testing and was responsible for releasing Rustup.}
            \zh{改善 Rustup 测试，负责发布 Rustup。}
      \item \en{Added UI tests for Rustup and successfully upgraded the clap dependency.}
            \zh{为 Rustup 添加了 UI 测试，顺利升级了 clap 依赖。}
      \item \en{Replaced term dependency with termcolor to fix the color display problem in MSYS2 terminal.}
            \zh{将 term 依赖替换为 termcolor，修复了 MSYS2 终端下颜色显示的问题。}
      \item \en{Responsible for the daily maintenance of the project, including code review, security vulnerability fixing, etc.}
            \zh{负责项目日常维护，包括代码审查、依赖升级、安全漏洞修复等。}
\end{itemize}

\en{\datedsubsection{\textbf{ant-design - Previous Maintainer}}{{\href{https://github.com/ant-design/ant-design/commits?author=hi-rustin}{24+ commits}}}}
\zh{\datedsubsection{\textbf{ant-design - 前维护者}}{{\href{https://github.com/ant-design/ant-design/commits?author=hi-rustin}{24+ commits}}}}
\en{\textsl{An enterprise-class UI design language and React UI library.}}
\zh{\textsl{企业级 UI 设计语言和 React UI 库。}}

\begin{itemize}
      \item \en{Refactored Input component and added cleanup button.}
            \zh{重构了 Input 组件，添加清理按钮。}
      \item \en{Designed and added Skeleton component.}
            \zh{设计并添加了 Skeleton 组件。}
      \item \en{Wrote contribution guidelines to guide others to participate in community contributions.}
            \zh{编写了贡献指南，引导其他人参与社区贡献。}
\end{itemize}

\end{document}
